---
title: "Homework 1"
author: "Max Wagner"
date: "February 7, 2015"
output:
  word_document: default
  pdf_document: default
  html_document:
    highlight: espresso
    theme: flatly
---
***

####10.

a0 = 50,000
an+1 = 0.01 * an - 1000

solving in R:

```{r}
i = 50000
n = 0
while (i > 1000) {
  i = (i * 1.01) - 1000
  n = n + 1
}
```

On month `r n`, they will be left with `r round(i, 2)` dollars

####9.

Solving in R:

```{r}
n <- c(1:16)
an <- c(3,6,11,21,32,47,65,87,112,140,171,204,241,282,325,376)
delta <- c(diff(an), NA)
plot(n, delta)
```

The graph appears to be mostly linear, with a little variation. The slope is roughly 3, which gives a rough equation of:

`delta_an = 3an`

```{r}
approx <- c(1:16) * 3
diff <- c(delta[1:15] - approx[1:15], NA)
plot(n, diff)
```

The differences are typically from 1 to -1, with an outlier at n = 15, where the difference is 6. The model fits reasonably for the purposes of this assignment.

####13.

```{r}
k <- .001
r <- 4
n <- 0
while (r < 999) {
  r <- r + ((k * r) * (1000 - r))
  n <- n + 1
  print(c(n,r))
}
```

The table above shows that it would take 11 periods for all 1000 people to hear the rumor.

####6.

a. The underlying idea of the models is that at a price of 100, and a quantity of 500, neither value will change. When price is above 100, quantity will increase by the growth factor 0.2, when quanity is above 500, price will decrease by a growth factor of -0.1. Typically when price increases, quantity decreases, so the first part is a bit odd. But the equilibrium point of the price of 100, and quantity of 500 remains the same regardless.

Case A:

```{r}
p <- 110
q <- 500
for (i in 1:10) {
  p <- p - .1 * (q - 500)
  q <- q + .2 * (p - 100)
  print(c(p, q))
}
```

Case B:

```{r}
p <- 200
q <- 500
for (i in 1:10) {
  p <- p - .1 * (q - 500)
  q <- q + .2 * (p - 100)
  print(c(p, q))
}
```

Case C:

```{r}
p <- 100
q <- 600
for (i in 1:10) {
  p <- p - .1 * (q - 500)
  q <- q + .2 * (p - 100)
  print(c(p, q))
}
```

Case D:

```{r}
p <- 100
q <- 400
for (i in 1:10) {
  p <- p - .1 * (q - 500)
  q <- q + .2 * (p - 100)
  print(c(p, q))
}
```