---
title: "Homework 11"
author: "Max Wagner"
date: "April 14, 2016"
header-includes:
   - \usepackage{bbm}
output:
  pdf_document: default
  html_document:
    highlight: espresso
    theme: flatly
  word_document: default
---
***


##529.1

$$ x = -e^t, y = e^t $$ 

$$ \frac{dx}{dt} = -y, \frac{dy}{dt} = -x $$

$$ \frac{dx}{dt} = -e^t, y = e^t, \frac{dx}{dt} = -y $$ 

$$ \frac{dy}{dt} = e^t, x = -e^t, \frac{dy}{dt} = -x $$


##529.6

$\frac{dx}{dt}$ and $\frac{dy}{dt}$ = 0 at (2,1)

Finding other points can be done with $rcos(\theta), rsin(\theta)$ where r is the radius from the stable point (2,1), and theta is the angle from (2,1).


##536.7

a.

$$ \frac{dx}{dt} = (a-by)x, \frac{dy}{dt} = (m-nx)y $$

$$ \frac{dy}{dx} = \frac{(m-nx)y}{(a-by)x} $$

b.

integrating gives:

$$ \frac{y(m ln(x) - nx)}{a-by} + K $$

exponetiation gives

$$ y^a e^{-by} = Kx^m e^{-nx} $$


##546.1

$$ f(y) = \frac{y^a}{e^{by}} $$

$$ f'(y) = \frac{y^{a-1}(by-a)}{e^{by}} $$

Setting $f'(y) = 0$ gives:

$$ y = a / b $$

This means that the above is a critical point, but we are unsure if its a maxima or minima. Let's take the 2nd derivative.

$$ f''(y) = \frac{y^{a-2}(b^2y^2 - 2aby + a^2 - a)}{e^{by}} $$

We can then substitute y for a / b, but it becomes impossible to assign a maxima or minima without knowing `a` and `b`. The end result is we know we have a critical point at (2,1), but we do not know if it a max or min.


## 566.1

Not really sure how to do this at the moment with an immense amount of work. Working on figuring it out...

A potential solution is:

x:

```{r}
x1 <- matrix(c(1,.985,.97,1,.925,.85), ncol = 2)
x1
x2 <- matrix(c(1,.99,.97,1,.95,.9017), ncol = 2)
x2
```

y:

```{r}
y1 <- matrix(c(1,.985,.97,1,.925,.85), ncol = 2)
y1
y2 <- matrix(c(1,.99,.98,1,.95,.9013), ncol = 2)
y2
```